---
title: "For solve the questions of chapter4 in ISLR"
author: "*Kiseong Park; Doctor, Data scientist*"
date: "*Friday, April 26, 2019*"
output: html_notebook
---

**Question 10.**    
This question needs 'Weekly' data from ISLR package.

```{r}
library(ISLR)
head(Weekly)
summary(Weekly)
```

*Exploratory data analysis*

```{r}
library(dplyr)
library(ggplot2)
ggplot(Weekly, aes(Year, fill=Direction)) + geom_bar()

ggplot(Weekly, aes(Lag1, fill=Direction)) + geom_density(alpha=0.5)
ggplot(Weekly, aes(Lag2, fill=Direction)) + geom_density(alpha=0.5) 
ggplot(Weekly, aes(Lag3, fill=Direction)) + geom_density(alpha=0.5) 
ggplot(Weekly, aes(Lag4, fill=Direction)) + geom_density(alpha=0.5) 
ggplot(Weekly, aes(Lag5, fill=Direction)) + geom_density(alpha=0.5) 
ggplot(Weekly, aes(Volume, fill=Direction)) + geom_density(alpha=0.5) 
ggplot(Weekly, aes(Today, fill=Direction)) + geom_density(alpha=0.5) 

cor(Weekly[,-9])
source("C:/Users/KS-Park/OneDrive/Documents/panel.cor.R")
pairs(Weekly, upper.panel = panel.cor)
```

*GLM*

```{r}
wk.glm <- glm(Direction ~ Lag1 + Lag2 + Lag3 + Lag4 + Lag5 + Volume, data=Weekly, family='binomial')
wk.glm %>% summary() 

yhat_glm <- predict(wk.glm, type='response')
pred_glm <- rep('Down', 1089)
pred_glm[yhat_glm > 0.5] <- 'Up'
table(Weekly$Direction, pred_glm)

Acc_glm <- (54+557)/1089
Acc_glm

Wk.test <- Weekly %>%
  filter(Year == 2009 | Year == 2010)

Wk.training <- setdiff(Weekly, Wk.test)

yhat_glm2.t <- predict(wk.glm2, newdata=Wk.test, type='response')
yhat_pred2.t <- rep('Down', 104)
yhat_pred2.t[yhat_glm2.t >0.5] <- 'Up'
table(Wk.test$Direction, yhat_pred2.t)

Acc_glm2 <- (9+56)/104
Acc_glm2
```

*LDA*

```{r}
Wk.lda <- lda(Direction ~ Lag2, Wk.training)
Wk.lda

yhat_lda <- predict(Wk.lda, newdata = Wk.test)
table(Wk.test$Direction, yhat_lda$class)

Acc_lda <-(9+56)/104 
Acc_lda
```

*QDA*

```{r}
Wk.qda <- qda(Direction ~ Lag2, Wk.training)
Wk.qda
yhat_qda <- predict(Wk.qda, newdata = Wk.test)
table(Wk.test$Direction, yhat_qda$class)

Acc_qda <- (0+61)/104
Acc_qda
```

*KNN*

```{r}
library(class)

set.seed(0426)
yhat_knn <- knn(as.matrix(Wk.training[,3]), as.matrix(Wk.test[,3]), Wk.training[,9], k=1)
table(Wk.test$Direction, yhat_knn)

Acc_knn <- (21+32)/104
Acc_knn
```

*Model selection*

```{r}
c(Acc_glm2, Acc_lda, Acc_qda, Acc_knn)
```

Logistric regression and LDA show best accuracy in these analysis.

* For another K*

```{r}
library(class)

set.seed(0426)
yhat_knn3 <- knn(as.matrix(Wk.training[,3]), as.matrix(Wk.test[,3]), Wk.training[,9], k=3)
table(Wk.test$Direction, yhat_knn3)

Acc_knn3 <- (15+42)/104
Acc_knn3

yhat_knn100 <- knn(as.matrix(Wk.training[,3]), as.matrix(Wk.test[,3]), Wk.training[,9], k=100)
table(Wk.test$Direction, yhat_knn100)

Acc_knn100 <- (21+32)/104
Acc_knn100
```


**Question 11**

This question need 'Auto' data in ISLR package.

```{r}
library(ISLR)
glimpse(Auto)
summary(Auto)

auto <- Auto
auto$mpg01 <- ifelse(auto$mpg >= median(auto$mpg), 1, 0)

cor(auto[,-9])
pairs(auto, upper.panel = panel.cor)

ggplot(auto, aes(factor(mpg01), cylinders)) + geom_boxplot()
ggplot(auto, aes(factor(mpg01), displacement)) + geom_boxplot()
ggplot(auto, aes(factor(mpg01), horsepower)) + geom_boxplot()
ggplot(auto, aes(factor(mpg01), weight)) + geom_boxplot()
```

*Split datasets*

```{r}
n <- nrow(auto)
idx <- 1:n
training_idx <- sample(idx, n*0.6)
validation_idx <- setdiff(idx, training_idx)
training <- auto[training_idx,]
validation <- auto[validation_idx,]
```

*LDA*

```{r}
auto.lda <- lda(mpg01 ~ cylinders + displacement + horsepower + weight, training)
auto.lda

auto_lda.yhat <- predict(auto.lda, newdata = validation)
table(validation$mpg01, auto_lda.yhat$class)

Acc_auto.lda <- (67+76)/157
Acc_auto.lda
```

*QDA*

```{r}
auto.qda <- qda(mpg01 ~ cylinders + displacement + horsepower + weight, training)
auto.qda

auto_qda.yhat <- predict(auto.qda, newdata = validation)
table(validation$mpg01, auto_qda.yhat$class)

Acc_auto.qda <- (69+73)/157
Acc_auto.qda
```

*Logistric Regression*

```{r}
auto.glm <- glm(mpg01 ~ cylinders + displacement + horsepower + weight, training, family='binomial')
auto.glm %>% summary()

auto_glm.yhat <- predict(auto.glm, newdata = validation, type='response')
glm_pred <- rep('Down', 157)
glm_pred[auto_glm.yhat > .5] <- 'Up'
table(validation$mpg01, glm_pred)

Acc_auto.glm <- (66+73)/157
Acc_auto.glm
```

*KNN*

```{r}
library(class)

set.seed(0426)
auto_knn.yhat <- knn(training[,2:5], validation[,2:5], training[,10], k=70)
table(validation$mpg01, auto_knn.yhat)

Acc_knn1 <- (64 + 71)/157
Acc_knn1

Acc_knn3 <- (65 + 73)/157
Acc_knn3

Acc_knn10 <- (65 + 76)/157
Acc_knn10

Acc_knn30 <- (68 + 74)/157
Acc_knn30
```

**Question 12**

```{r}
Power <- function(a){
  2^a
}

Power2 <- function(x,a){
  x^a
}

Power2(131,3)

Power3 <- function(x,a){
  result <- x^a
  return(result)
}

x <- seq(1, 10, 0.1)
y <- Power3(x,2)
plot(x, y, log='xy')

PlotPower <- function(x,a){
  y <- x^a
  plot(x, y)
}

PlotPower(1:10,3)
```

**Question 13**

This question needs 'Boston' data.

```{r}
glimpse(Boston)
boston <- Boston
boston$crim01 <- ifelse(boston$crim >= median(boston$crim), 1, 0)
```


```{r}
cor(boston[,-1])
pairs(boston[,-1], upper.panel = panel.cor)
```

`indus` + `nox` + `age` + `dis` + `tax` have strong relastions with `crim01`.

```{r}
n_boston <- nrow(boston)
boston_idx <- 1:n_boston
b.training_idx <- sample(boston_idx, n*0.7)
b.validation_idx <- setdiff(boston_idx, b.training_idx)
b.training <- boston[b.training_idx,]
b.validation <- boston[b.validation_idx,]
```

*GLM*

```{r}
bs.glm <- glm(crim01 ~ indus + nox + age + dis + tax, data = b.training, family='binomial')
bs.glm %>% summary()

bs.yprob_glm <- predict(bs.glm, newdata = b.validation, type='response')
bs.yhat_glm <- ifelse(bs.yprob_glm >= 0.5, 1, 0)
table(b.validation$crim01, bs.yhat_glm)
mean(b.validation$crim01 == bs.yhat_glm)
```

*LDA*

```{r}
bs.lda <- lda(crim01 ~ indus + nox + age + dis + tax, data = b.training)
bs.lda

bs.yhat_lda <- predict(bs.lda, newdata = b.validation)
table(b.validation$crim01, bs.yhat_lda$class)
mean(b.validation$crim01 == bs.yhat_lda$class)
```

*QDA*

```{r}
bs.qda <- qda(crim01 ~ indus + nox + age + dis + tax, data = b.training)
bs.qda

bs.yhat_qda <- predict(bs.qda, newdata = b.validation)
table(b.validation$crim01, bs.yhat_qda$class)
mean(b.validation$crim01 == bs.yhat_qda$class)
```

*KNN*

```{r}
bs.yhat_knn <- knn(b.training[,c(3,5,7,8,10)], b.validation[,c(3,5,7,8,10)], b.training[,15], k=3)

table(b.validation$crim01, bs.yhat_knn)
mean(b.validation$crim01 == bs.yhat_knn)
```

